Leadership across cultures and contexts: an exploratory analysis

### 2020-04-04 leadership_across_cultures_contexts.Rmd
Added https to doi. More detail on PSF. Add info on correlation between pages and text records, incl. scatter plot.

We estimate the cross-cultural frequency in the functions and qualities of leaders and the costs and benefits of leadership for both leaders and followers using an ethnographic database previously built and published (doi.org/10.5281/zenodo.2541999), from which @garfield_evolutionary_2019 "tested" three theoretical models against the ethnographic record. The electronic Human Relations Area Files (eHRAF) is a digital collection of ethnographies, subject-coded at teh paragraph level following a the Outline of Cultural Materials (OCM) coding scheme. The eHRAF is a subset of the larger HRAF and is continually growing in scope.

Whereas @garfield_evolutionary_2019, documented supporting evidence for measures of leadership in reference to influential theoretical models, our goals here are to let the ethnographic record "speak for itself" in understanding variation in the dimensions of leadership we are interested in, i.e., our methods and analyses are exploratory and not strictly theoretically driven. We draw on the same database of `r nrow(leader_text2)` ethnographic paragraphs (termed text records) extracted from the 60-culture Probability Sample Files (PSF) of the eHRAF database [@naroll_proposed_1967]. The latter comprises over `r trunc(sum(dfwc$`N Pages eHRAF`)/1000)`K pages of digitized text.

@@

The geographic distribution of the cultures in our sample is displayed in Figure \@ref(fig:geographic), with cultures labeled by mode of subsistence and represented by a symbol proportional to the number of documents that provide ethnographic texts for that culture. The `r nrow(leader_text2)` text records from `r length(unique(leadershipdata::documents$d_ID))` unique documents describing `r length(unique(leader_text2$d_culture))` cultures were generally short, ranging from `r textstats$min` to `r textstats$max` words, with a median word count of `r textstats$median`, a mean of `r textstats$mean`, and standard deviation of `r textstats$sd`. Of the `r nrow(leader_text2)` text records, `r final_record_count` had evidence for at least one variable in the study.

@@

>>>>

We estimate the cross-cultural frequency in the functions and qualities of leaders and the costs and benefits of leadership for both leaders and followers using an ethnographic database previously built and published (https://doi.org/10.5281/zenodo.2541999), from which @garfield_evolutionary_2019 "tested" three theoretical models against the ethnographic record. The electronic Human Relations Area Files (eHRAF) is a digital collection of ethnographies, subject-coded at teh paragraph level following a the Outline of Cultural Materials (OCM) coding scheme. The eHRAF is a subset of the larger HRAF and is continually growing in scope.

Whereas @garfield_evolutionary_2019, documented supporting evidence for measures of leadership in reference to influential theoretical models, our goals here are to let the ethnographic record "speak for itself" in understanding variation in the dimensions of leadership we are interested in, i.e., our methods and analyses are exploratory and not strictly theoretically driven. We draw on the same database of `r nrow(leader_text2)` ethnographic paragraphs (termed text records) extracted from the 60-culture Probability Sample Files (PSF) of the eHRAF database [@naroll_proposed_1967]. The PSF aims to mitigate Galton's problem by randomly sampling of one culture with high quality ethographic coverage from each of 60 culture regions. It comprises over `r trunc(sum(dfwc['N Pages eHRAF'])/1000)`K pages of digitized text.

@@

The geographic distribution of the cultures in our sample is displayed in Figure \@ref(fig:geographic), with cultures labeled by mode of subsistence and represented by a symbol proportional to the number of documents that provided ethnographic texts for that culture. The `r nrow(leader_text2)` text records from `r length(unique(leadershipdata::documents$d_ID))` unique documents describing `r length(unique(leader_text2$d_culture))` cultures were generally short, ranging from `r textstats$min` to `r textstats$max` words, with a median word count of `r textstats$median`, a mean of `r textstats$mean`, and standard deviation of `r textstats$sd`. Of the `r nrow(leader_text2)` text records, `r final_record_count` had evidence for at least one variable in the study.

```{r corpus}
cor_pages_tr <- cor.test(~number_leader_records + `N Pages eHRAF`, dfwc)
```

There was a weak positive relationship between the number of leader text records we retrieved from each culture and the total number of pages of ethnography for each culture in eHRAF (r = `r signif(cor_pages_tr$estimate, 2)`, p = `r signif(cor_pages_tr$p.value, 2)`). A loess regression suggested that the number of records initially increased with the total number of pages of ethnography, plateauing at about 35 records around 4500 pages (see Figure \@ref(fig:eHRAFpages)).

@@

# Supplementary information

```{r eHRAFpages, fig.height=6, fig.cap="Scatterplot of the number of leadership text records versus the total number of pages of ethnography in the eHRAF. Each dot is one culture. Line fit by loess regression."}
plot_pages_tr
```
